### 2017-10-19 paper/sections/6_results.tex
paper: add graph for partial updates
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb] \centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png} \caption{
[\href{https://...}{source}] Slowdown of a single client periodically syncing
updates to the gobal namespace. The crossover point represents the trade-off of
frequent updates of small journal files and infrequent updates of large journal
files.\ref{fig:slowdown-sync}.  \label{fig:slowdown-sync}} \end{figure}

% Does this implementation need to be described in the implementation?
Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing updates to a decoupled namespace and pausing to send updates to
the metadata server. We scale the namespace sync interval to show the trade-off
of frequently pausing or writing large logs of updates.  We use an idle core to
log the updates and to do the network transfer. The client only pauses to fork
off a background process, which is expensive as the address space needs to
copied. The alternative is to pause the client completely and write the update
to disk but since this implementation is limited by the speed of the disk, we
choose the memory-to-memory copy of the fork appraoch.`

To show the contention at the metadata server, we scale the number of
concurrent journal merge events in FigureX. The size of each journal is 100K
files, the maximum recommended directory size for CephFS. We also plot the cost
of RPCs with and without journaling.

>>>>

\begin{figure}[tb] \centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png} \caption{
[\href{https://...}{source}] Slowdown of a single client periodically syncing
updates to the gobal namespace. The crossover point represents the trade-off of
frequent updates (with small journal files) and infrequent updates (with larger journal
files).\ref{fig:slowdown-sync}.  \label{fig:slowdown-sync}} \end{figure}

% Does this implementation need to be described in the implementation?
Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing updates to a decoupled namespace and pausing to send updates to
the metadata server. We scale the namespace sync interval to show the trade-off
of frequently pausing or writing large logs of updates.  We use an idle core to
log the updates and to do the network transfer. The client only pauses to fork
off a background process, which is expensive as the address space needs to
copied. The alternative is to pause the client completely and write the update
to disk but since this implementation is limited by the speed of the disk, we
choose the memory-to-memory copy of the fork approach.

To show the contention at the metadata server of this approach, we scale the
number of concurrent journal merge events in FigureX. The size of each journal
is 100K files, the maximum recommended directory size for CephFS. We also plot
the cost of RPCs with and without journaling.
